Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-12 implementation.tex
Edited section 3
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1040 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we describe an implementation of the \lloid\ method described
in section \ref{sec:method} suitable for rapid \GW{}
searches for \CBC{}s.  The \lloid\ method requires several
computations that can be completed before the analysis is underway.  Thus
we divide the procedure into two stages 1) an off-line planning stage and 2) an
online, low-latency filtering stage.  The off-line stage can be done before the
analysis is started and updated asynchronously, whereas the online stage must
keep up with the detector output and produce search results as rapidly as
possible.  In the next two subsections we describe what these stages entail.

>>>>

In this section we describe an implementation of the \lloid\ method described
in section \ref{sec:method} suitable for rapid \GW{}
searches for \CBC{}s.  The \lloid\ method requires several
computations that can be completed before the analysis is underway.  Thus
we divide the procedure into an offline planning stage and an
online, low-latency filtering stage.  The offline stage can be done before the
analysis is started and updated asynchronously, whereas the online stage must
keep up with the detector output and produce search results as rapidly as
possible.  In the next two subsections we describe what these stages entail.
